Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-15 paper/paper.tex
adding abstract in a different file to facilitate last-minute word counting

%% JavaScript (\js{}) is a popular programming language for the
%% web. Finding errors in JS runtime engines is an important problem.
\begin{abstract}
JavaScript is a very popular programming language today, permeating
different domains of application. Several JavaScript engines compete
for dominance and bugs on these engines are not rare. One important
reason for that is the language specification, which is incomplete and
evolves frequently.

This paper reports on a study to assess reliability
of JavaScript engines by leveraging the rich diversity of open-source
implementations. For that, we explored two methods---test
transplantation and cross-engine differential testing. Test
transplantation evaluates the effects of running test suites of a given
engine in another engine. Cross-engine differential testing evaluates
the effects of fuzzing existing inputs and then comparing the output
produced by different engines with a differential oracle.

Our results indicate that \Fix{...}
\end{abstract}

>>>>

%% JavaScript (\js{}) is a popular programming language for the
%% web. Finding errors in JS runtime engines is an important problem.
\begin{abstract}
  \input{abstract}
\end{abstract}
